### 2019-02-13 sections/relatedwork.tex

>>>>

\subsection{Functional Reactive Programming}

Functional Reactive Programming (FRP) is a paradigm to describe graphs of values, called behaviors, that depend on each other and on external events.
Behaviors can change over time, or triggered by events.
When a behavior changes, all other behaviors that depend on it are updated automatically.

There are some concepts that are similar in \TOP and FRP.
The \emph{stepper} behavior is associated with an event and yields the value of the most recent event.
This is similar to editors in \TOP.
